Summary of PM2.5 Nonattainment  Analysis

### 2020-11-08 Analysis Files/Paper_Analysis_zigler.Rmd
adding our paper analyisis rmd file

```{r}
rm(list=ls())
set.seed(51)
# library(HEIfunctions)
library(maps)
library(PSAgraphics)
library(data.table)

@@

#########   Read in the data and define baseline and follow up measures    ##########
#### Read in the Data ######
# --- 'pmanalysis.RData' is a file created from the data construction files
# ---  Use this file if you want to see the whole analysis from start to finish
# ---  But note that the data sets and results produced with this file will be different
# --- from those reported in the paper (sample size, propensity score estimates, effect estimates, etc.).
# ---  This is because all of the Medicare data are simulated
load(file="pmanalysis.RData")

>>>>

```{r, echo=FALSE}
rm(list=ls())
set.seed(51)
library(HEIfunctions)
library(maps)
library(PSAgraphics)
library(data.table)

@@

#########   Read in the data and define baseline and follow up measures    ##########
#### Read in the Data ######
# --- 'pmanalysis.RData' is a file created from the data construction files
# ---  Use this file if you want to see the whole analysis from start to finish
# ---  But note that the data sets and results produced with this file will be different
# --- from those reported in the paper (sample size, propensity score estimates, effect estimates, etc.).
# ---  This is because all of the Medicare data are simulated
load(file="Data Construction/pmanalysis.RData")
